---
title: "Projects"
format: html
---

# Coding

Using skills learned in An Bui's Statistics for Environmental Studies course, I tracked my personal data and made a corresponding visualization. I tracked the amount of caffeine I consumed each day in mg, and compared it with the number of classes I attended in that specific day, among other variables. A boxplot and jitterplot are displayed on the same graph to display summarized and underlying data. 

I learned that my consumption generally

```{r setup, message=FALSE}
#| echo: false
library(tidyverse)
library(here)
library(gt)
library(janitor)
library(readxl)
library(dplyr)
mydata <- read_csv("ENVS-193DS_caffeine_hw2.csv")
```

```{r}
#| echo: false
# data wrangling
mydata_clean <- mydata |> # start mydata dataset
  filter(Classes %in% c("0", "1", "2")) |> # filter for 0, 1, or 2 classes
  mutate(Classes = as_factor(Classes)) |> # make sure classes (numerical) are being read in as a factor
  select(Classes, `Caffeine (mg)`, Ounces) |> # select columns of interest
  rename(caffeine_mg = `Caffeine (mg)`) # renaming caffeine column for ease
```

```{r}
#| echo: false
# plot creation
ggplot(data = mydata_clean, # using the clean dataset
       aes(x = Classes, # setting x axis as classes
           y = caffeine_mg, # setting y axis as caffeine in mg
           color = Classes, # coloring by classes, so 0/1/2 have their own colors
           shape = Classes, # making sure 0/1/2 have their own shapes
          fill = Classes)) + # making sure 0/1/2 are filled with color
  geom_boxplot() + # making boxplots
  geom_jitter(height = 0, # making sure the points don't move vertically
              width = 0.1) + # limiting how much the points move horizontally
  labs(y = "Caffeine (mg)") + # relabeling the y-axis
  theme_get() + # changing the theme
  scale_color_manual(values = c("0" = "darkgreen", # manually coloring 0, 1, and 2
                                "1" = "tan3",
                                "2" = "chocolate4")) +
   scale_shape_manual(values = c("0" = 17, "1" = 18, "2" = 19)) + # making data points different shapes
  scale_fill_manual(values = c("0" = "#99b99d", 
                               "1" = "#e9c76b", 
                               "2" = "#c2a47e")) # filling in boxplots
```


# Testimony

In this testimony project, my partner and I created and recited a written piece of legislation advocating for co-management of public lands with Indigenous people, specifically in Yosemite and Great Smokies National Parks. This project truly encapsulated how informative this course is, which would not be the same if not taught by Professor Deborah Williams. Extensive research was done with her support. Practice of a testimony speech with follow-up questions under simulated and timed conditions tested our preparation and expertise on the topic. 


<iframe src="docs/pdfs/ENVS-159_Written_Testimony.pdf" width="100%" height="600px">